Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2011-01-12 results.tex
Some type fixes
Rev1: initial fixes

Next we would like to illustrate the role of anisotropic mesh refinements.
Figs.~\ref{fig:isoanisodof} and \ref{fig:isoanisocpu} show typical results 
for the H\_ISO, H\_ANISO, HP\_ISO, HP\_ANISO adaptivity modes in terms 
of DOF and cumulative CPU time.

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{isoaniso_dof}
  \caption{\label{fig:isoanisodof} Number of DOF as a function of physical time for 
  multi-mesh configurations with H\_ISO, H\_ANISO,
  HP\_ISO, and HP\_ANISO adaptivity modes.}
  \end{centering}
\end{figure}

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{isoaniso_cpu}
  \caption{\label{fig:isoanisocpu} Cumulative CPU time as a function of physical time 
  for multi-mesh configurations with H\_ISO, H\_ANISO,
  HP\_ISO, and HP\_ANISO adaptivity modes.}
  \end{centering}
\end{figure}

@@

\subsection{Time stpe control of HP\_ANISO adaptivity}

>>>>

Next we would like to illustrate the role of anisotropic mesh refinements.
Figs.~\ref{fig:isoanisodof} and \ref{fig:isoanisocpu} show typical results 
for the HP\_ISO, HP\_ANISO\_H,  HP\_ANISO adaptivity modes in terms 
of DOF and cumulative CPU time.

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{isoaniso_dof}
  \caption{\label{fig:isoanisodof} Number of DOF as a function of physical time for 
  multi-mesh configurations with HP\_ANISO,
  HP\_ANISO\_H, and HP\_ISO adaptivity modes.}
  \end{centering}
\end{figure}

\begin{figure}[!ht]
  \begin{centering}
  \includegraphics[width=\columnwidth]{isoaniso_cpu}
  \caption{\label{fig:isoanisocpu} Cumulative CPU time as a function of physical time 
  for multi-mesh configurations with HP\_ANISO,
  HP\_ANISO\_H, and HP\_ISO adaptivity modes.}
  \end{centering}
\end{figure}

@@

\subsection{Time step control of HP\_ANISO adaptivity}
